RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2014-11-21 manuscripts/manuscript.Rmd
Fix the add_basic_meta argument order

```{r}
data(bird.orders)
birds <- add_trees(bird.orders)
birds <- add_basic_meta(birds,
  title = "Phylogeny of the Orders of Birds From Sibley and Ahlquist",

@@

  creator = "Sibley, C. G. and Ahlquist, J. E.")
```

@@

```{r}
birds <- add_basic_meta(birds, citation = citation("ape"))
```

@@

```{r}
library("knitcitations")
geiger_nex <- add_basic_meta(geiger_nex, citation = bib_metadata("10.2307/2408428"))
```

>>>>

```{r}
data(bird.orders)
birds <- add_trees(bird.orders)
birds <- add_basic_meta(
  title = "Phylogeny of the Orders of Birds From Sibley and Ahlquist",

@@

  creator = "Sibley, C. G. and Ahlquist, J. E.",
  nexml = birds)
```

@@

```{r}
birds <- add_basic_meta(citation = citation("ape"), nexml=birds)
```

@@

```{r}
library("knitcitations")
geiger_nex <- add_basic_meta(citation = bib_metadata("10.2307/2408428"), nexml=geiger_nex)
```
